---
title: "Assignment 02"
author: "Scott Stoltzman"
date: "5/12/2019"
output: html_document
---

Install package: 'nycflights123'

```{r}
library('nycflights13')
library('tidyverse')
```


### Answer the problems below in the spaces between `<ANSWER BELOW>` and `<ANSWER ABOVE>`

## Practice

1.  Why does this code not work?

    ```{r, error = TRUE}
    my_variable <- 10
    my_varıable
    ```
    
    Look carefully! (This may seem like an exercise in pointlessness, but
    training your brain to notice even the tiniest difference will pay off
    when programming.)
    
    
    `<ANSWER BELOW>`
    PUT YOUR ANSWER HERE
    `<ANSWER ABOVE>`
    
    
1.  Press Alt + Shift + K. What happens? How can you get to the same place
    using the menus?


    `<ANSWER BELOW>`
    PUT YOUR ANSWER HERE
    `<ANSWER ABOVE>`



Find all flights that  

  1. Had an arrival delay of two or more hours  
  2. Flew to Houston (IAH or HOU)
  3. Were operated by United, American, or Delta
  4. Departed in summer (July, August, and September)
  5. Arrived more than two hours late, but didn’t leave late
  6. Were delayed by at least an hour, but made up over 30 minutes in flight
  7. Departed between midnight and 6am (inclusive)

```{r}

```


Another useful dplyr filtering helper is between(). What does it do? Can you use it to simplify the code needed to answer the previous challenges?
```{r}

```


How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
```{r}

```

Why is NA ^ 0 not missing? Why is NA | TRUE not missing? Why is FALSE & NA not missing? Can you figure out the general rule? (NA * 0 is a tricky counterexample!)
```{r}

```

